Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-03-16 docs/ms.tex
Update ms.tex

@@

While making the posterior samples $p(\g,\alpha|Data) we choose to use the classical
Gibbs sampler.

>>>>

why is weak lensing important?
Weak gravitational lensing has become the most potential tool for constraining the cosmological parameters that describe the dark universe (Albrecht et al. 2006; Peacock & Schneider 2006). 
One application of Weak gravitational lensing is that it can be used to measure the mass profile of single galaxy,galaxy groups and clusters or large scales.

Cosmic shear is the mild distortion of distant galaxy images due to the
bending of light by intervening matter.

Cosmic shear provides one of the most promising methods for constraining the nature of
dark energy (Albrecht et al. 2006; Peacock&Schneider 2006).

What is the big problems of weak lensing analysis:
The magnitude of shear in Weak lensing is typically ~0.01 it's usually 10 times smaller than the intrinsic shape 
noise,it's also smaller than the distortion caused be PSF effect which usually has ~0.05 level.
We have little information about the intrinsic shape distribution futher than it's istropic,the direct observation we can make is mere the distribution
of lensed ellipticity.And there is an analytical fine model to describe intrinsic shape distribution.

how do we break it down to e measurement, and g inference, and cosmological parameter estimation?

The measurement of galaxy shapes from images is first step  of weak gravitational lensing analysis , since the observed ellipticities of distant galaxies are
Used to infer the shear map , which quantify how shape of galaxies are distorted.
The second step is to infer 
Finally,we can recover the projected mass profile of galaxies or dark energy by it’s shear map.

what are we studying in this paper (ie, not the whole thing, just going from es to gs).
In this paper we merely consider the inference of shear map from galaxies shape.
We set up an simple toy model in which we have the observed ellipticity as data,and the only measurement error we consider 
is a Gaussian noise add on the true lensed ellipticity.We suppose there is a uniform shear acting on one sky patch,

What approach will we take and WHY.

Our approach is to use an exceedingly model for intrinsic shape distribution,and use MCMC sampling to 
gives out the whole likelihood function of shear in many sky patches and their common shape parameters simultaneously.

We can use the credit interval of posterior samples as the uncertainty of estimate
, which can be used as statistical weights.It tells us how much information about shear can we obtain from observed data.

By doing this we use the information that galaxies in different sky patch should have the same intrinsic shape distribution.

@@

While making the posterior samples $p(\g,\alpha|Data)$ we choose to use the classical
Gibbs sampler.
